MLCommons Earthquake Science Benchmark

### 2022-02-19 paper-capstone-earthquake.tex
rewrite of hardware

\subsection{Aurora}
\label{id:anl}

The Aurora supercomputer, sponsored by the U.S. Department of Energy
(DOE), is part of the Argonne Leadership Computing Facility (ACLF). It
was developed with the help of industry experts from Intel and
Cray. Aurora offers HPC for data analytics and AI development with a
peak performance of over 2 Exaflop DP. The system is based on the HPE
Cray EX supercomputer platform and offers over 9,000 compute nodes.

Argonne National Laboratory (ANL), ... \cite{www-aurora}

\subsection{Summit}
\label{id:ornl}

The Summit supercomputer, sponsored by the U.S. Department of Energy
(DOE), is located in the Oak Ridge Leadership Computing Facility
(OLCF). The open science computing system is available to government,
academic, and industry researchers to solve complex problems in all
fields of science. The system is powered by 4,608 nodes which each
house multiple IBM POWER9 CPUs and NVIDIA Volta GPUs on top of half a
terabyte of coherent memory.

Oak Ridge National Laboratory (ORNL), Summit \cite{www-summit}

\subsection{Perlmutter}
\label{id:nersc}

The Perlmutter supercomputer, sponsored by the U.S. Department of
Energy (DOE), is located in Shyh Wang Hall at Berkeley Lab and is
operated by the National Energy Research Scientific Computing Center
(NERSC). The supercomputer has a 12 cabinet GPU systems with over
1,500 nodes and a 12 cabinet CPU system containing over 3,000
nodes. It is supported by 35 petabytes of all-flash storage which can
move data at 5 terabytes/sec.

National Energy Research Scientific Computing Center (NERSC), ...
\cite{www-perlmutter}

\subsection{SDSC}
\label{id:sdsc} 
\TODO{Which of the SDSC systems will we be benchmarking?}
San Diego Super Computing Center, ... \cite{www-expanse}

\subsection{University of Virginia Rivanna}
\label{id:uva}

@@

The PEARL system, funded by the Alan Turing Institute, is hosted at
the Rutherford Appleton Laboratory by the Science and Technology
Facilities Council (STFC). It was developed for the advancement of AI
and Machine Learning research with large-scale scientific datasets,
already contributing to the fields of materials, environmental and
life sciences, and astronomy. It is comprised of two NVIDIA DGX2
nodes, 32 GPUs, 3TB of system memory, 1TB of GPU memory, and 600TB of
high-speed storage.

Rutherford Appleton Laboratory (RAL), UK 
Pearl \cite{www-pearl-1}

@@

The NVIDIA DGX Station A100 is a commercially available product that
can provide powerful computing resources to all industries. The DGX
Station is an AI resource that can run parallel jobs and support
training, inference, and data analytics. It contains 4 NVIDIA A100
GPUs and up to 320 GBs of GPU memory. With the use of Multi-Instance
GPU (MIG), each A100 GPU can be partitioned into 7 isolated instances.

DGX Fox \cite{www-dgx-station-a100}

>>>>

\subsubsection{Aurora}
\label{id:anl}

The Aurora supercomputer \cite{www-aurora} is locatd at that Argonne
Leadership Computing Facility (ACLF) part of the U.S. Department of
Energy (DOE).  It was developed with the help of industry experts from
Intel and Cray. Aurora offers HPC for data analytics and AI
development with a peak performance of over 2 Exaflop DP. The system
is based on the HPE Cray EX supercomputer platform and offers over
9,000 compute nodes.

\subsubsection{Summit}
\label{id:ornl}

The Summit supercomputer\cite{www-summit} is located in the Oak Ridge
Leadership Computing Facility (OLCF) part of the U.S. Department of
Energy (DOE). The system is avalable to government, academic, and
industry researchers to solve complex problems in all fields of
science. The system is powered by 4,608 nodes which each house
multiple IBM POWER9 CPUs and NVIDIA Volta GPUs on top of half a
terabyte of coherent memory.

\subsubsection{Perlmutter}
\label{id:nersc}

The Perlmutter \cite{www-perlmutter} supercomputer is located at the
National Energy Research Scientific Computing Center (NERSC) which is
part of the U.S. Department of Energy (DOE).  It has a 12 cabinet GPU
systems with over 1,500 nodes and a 12 cabinet CPU system containing
over 3,000 nodes \TODO{This is inconsistant or not properly explained
  as 2 node numbers are used}. It is supported by 35 petabytes of
all-flash storage which can move data at 5 terabytes/sec.

\subsubsection{Expanse}
\label{id:sdsc}

The Expanse \cite{www-expanse} system at the Sandiego Super Computing
Center (SDSC) ....

\TODO{Expanse description incomplete}

\subsubsection{Rivanna}
\label{id:uva}

University of Virginia Rivanna

\TODO{Rivann description is inomplete}

@@

The PEARL \cite{www-pearl-1} system is located t the Alan Turing
Institute in the the Rutherford Appleton Laboratory, UK.  It was
developed for the advancement of AI and Machine Learning research with
large-scale scientific datasets, already contributing to the fields of
materials, environmental and life sciences, and astronomy. It is
comprised of two NVIDIA DGX2 nodes, 32 GPUs, 3TB of system memory, 1TB
of GPU memory, and 600TB of high-speed storage.

@@

The NVIDIA DGX Station A100 \cite{www-dgx-station-a100} is a
commercially available product that can provide powerful computing
resources to all industries. The DGX Station is an AI resource that
can run parallel jobs and support training, inference, and data
analytics. It contains 4 NVIDIA A100 GPUs and up to 320 GBs of GPU
memory. With the use of Multi-Instance GPU (MIG), each A100 GPU can be
partitioned into 7 isolated instances.
